---
title: "Static drawr examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{static_drawr_examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7
)
```

```{r setup}
library(shinysense)
library(dplyr)
```



You can embed you-draw-it style charts in your rmarkdown reports or plain standalone HTML documents by using [`shinysense::drawr`](http://nickstrayer.me/shinysense/reference/drawr.html). The options work almost identical to how they do in [`shinydrawr`](http://nickstrayer.me/shinysense/reference/shinydrawr.html). 

To demo this let's generate a simple time series dataset for our charts: 

```{r}
plot_data <- tibble(
  x = 1:50, 
  value = sin(x)
)

plot_data
```


Now we can get into building our plots. We can start with the defaults.

```{r}
# Standard mode
drawr(
  plot_data,
  x_col = x,
  y_col = value,
  draw_start = 25 # Start obscuring data after x = 25
)
```

You can do things like change the colors of the lines:

```{r}
drawr(
  plot_data,
  x_col = x,
  y_col = value,
  draw_start = 25,
  data_line_color = 'red',
  drawn_line_color = 'green'
)
```


You can customize the axes ranges:

```{r}
drawr(
  plot_data,
  x_col = x,
  y_col = value,
  draw_start = 25,
  x_range = c(-5, 55),
  y_range = c(-5, 5)
)
```

You can give your plot a title and custom axis labels.

```{r}
drawr(
  plot_data,
  x_col = x,
  x_lab = 'time',
  y_col = value,
  y_lab = 'dollars',
  title = 'Guess the pattern!',
  draw_start = 35
)
```


You can even just have the user draw for fun. (Makes more sense when used with `shinydrawr` where data can be retrieved)


```{r}
drawr(
  plot_data,
  free_draw = TRUE,
  x_col = x,
  title = 'Free Drawr',
  y_range = c(-5,5),
)
```


For more information on all the options available visit the [shinysense website's documentation](http://nickstrayer.me/shinysense/reference/drawr.html) or simply run `?drawr` in your R console. 

